Social Network Analysis: Week 3: Degree and Centrality

### 2022-03-06 docs/3. SNA - Assignments/DRAFT_Week3-Distill-Blog_Degree-and-Centrality.Rmd
3.6.22 time for a walk

Smuggler's Bay Drink Recipe Book Index

@@

    Vertices:

    -   Drink Name

    -   Drink Ingredient

@@

Network Description

:   Nodes:

    Edges:

    Ties: Are a connection between Drink Names and
    Drink Ingredients. The network is undirected
    and unweighted. Undirected: because the
    relationship between Drink Names and Drink
    Ingredients lacks any sort of power dynamic.
    Edge weights could be added by including the
    amount of each ingredient required for each
    drink recipe.

@@

    Smuggler's Bay Edglist is long but
    uncomplicated: which means there are few ways
    to subset data to help answer our research
    question: ***what sort of relationships exist
    between the components ?*** Which makes Drink
    Ingredient Type edge attribute very useful.

- Whether or not there are edge attributes

that might be used to:

- subset data, or

- stack multiple networks.

@@

results\*, including:

1\. the relevant statistics and interpretation.

For example, explaining which node(s) are most
central and which are least central.

2\. Discuss (with any related evidence) whether or
not the node(s) behavior is in line with or
violates expectations based on the degree
centrality measure.

3\. What do you make of network density and
centralization measures?

4\. What about differences in the binary 100
million threshold network vs valued trade flows
network.

5.  Check tutorial for other ideas of results to
    discuss.

    *Provide at least two or three noteworthy
    results*, including:

<!-- -->

1.  the relevant statistics and interpretation.

    -   For example, explaining which **node(s)
        are most central and which are least
        central.**

2.  Discuss (with any related evidence) whether or
    not the **node(s) behavior is in line with or
    violates expectations based on the degree
    centrality measure.**

    1.  **What do you make of network density and
        centralization measures?**

>>>>

Network Description: Smuggler's Bay Drink Recipes

@@

    Vertex Attributes

    vertices = 274

    -   Nodes:

        Drink Name

        Drink Ingredient

    -   total edges= 671

        missing edges= 0

        non-missing edges= 0

@@

:   Ties: Are a connection between Drink Names and
    Drink Ingredients. The network is undirected
    and unweighted. Undirected: because the
    relationship between Drink Names and Drink
    Ingredients lacks any sort of power dynamic.
    Edge weights could be added by including the
    amount of each ingredient required for each
    drink recipe.

@@

    Smuggler's Bay Edglist is long but
    uncomplicated: which means there are few ways
    to subset data to help answer our research
    question: ***what sort of relationships exist
    between the components ?***

    Which makes the edge attribute really useful
    because subsetting network data by Drink
    Ingredient Type allows us to look at the
    ingredients in rum-based cocktails vs those in
    gin-based cocktails.

@@

**Network & Ego Network**

-   Network Transitivity: 1 or 0

```{=html}
<!-- -->
```
-   Reach-ability:

    -   Network: K Path Census

    -   Ego Network: Path / Distance

**Network stats VS Individual Node stats**

-   Network Density

-   Degree: Network vs Node

-   Degree Centrality: Network vs Node

    -   Most Central Nodes

    -   Least Central Nodes

    -   Centralization Score Break Down

    -   <div>

        -   \$res

        -   \$centralization

        -   \$theoretical_max

        </div>

**2. Node Behavior:** Degree Centrality Meastures

Is node(s) behavior in line with or violates
expectations based on the degree centrality
measure.
